### 2021-03-24 input/proposal.tex
wip complexity

\subsection{Complexity}
\label{sec:complexity}

\TODO{To rework, for there are more components now. Maybe do this
  along the description of the approach.}

@@

\textbf{The communication complexity} concerns the size and number of
messages required to reach optimal partitioning. In the average-case,
a process $i$ chosen uniformly at random among all processes creates a
logical partition. Its messages $\alpha_i$ propagate through the
network until reaching processes that belong to another partition
closer to them. This splits partitions in half in average. Overall,
the $a^{th}$ new partition comprises
\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
processes. This decreases every new partition until reaching $0$
processes per new partition: even the chosen process already belongs
to its optimal partition. The average number of messages per process
is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
  more messages (receipt bounded by $|O|$ as well).} Deleting the
$a^{th}$ partition generates the exact same number of messages than
the $a^{th}$ partition creation. \TODO{But what about echos?} In the
worst-case, every new partition includes all but one process belonging
to the previous partition. The total number of messages after the
$a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot a^2)$. As
for the average-case, the number of messages for the partition
deletion is identical to the number of messages of the corresponding
partition creation.

>>>>

\subsection{Complexity}

@@

\paragraph{Space.}
Each process needs to maintain a vector of versions the size of which
depends on the number of sources. In the worst case, the size of this
vector increases linearly with the number of distinct sources that
ever existed in the system. For the sake of last win order, processes
can never purge this vector from any entry. \TODO{Even when the
  process leaves the system.} Fortunately, scoped broadcast limits
message propagation to interested processes. A process at a side of
the system may never hear of a source at the other side of the
system. In turns, it may never have to maintain an entry for this
source. \TODO{This is application-dependent?}

\noindent Each process must also maintain the partition it belongs to,
along with its control informations. Among other, it must maintain a
path the size of which depends on the membership size of the
partition. In the worst case, this path includes the identity of every
process of the system that currently belong to the system. Eventually,
the size of this path increases linearly with the diameter of the
current partition. \TODO{assuming weight equals 1 \ldots}

\paragraph{\TODO{Time.}}
In terms of processing time, whatever the operation, it increases
linearly with the number of neighbors of the process. It scales well,
for the number of neighbors is commonly order of magnitude lower than
the number of processes in the system. For instance, random networks
only require $O(\log(|V|))$ neighbors to work properly \REF; and
processes in autonomous systems have in average \TODO{X} neighbors
\REF. Lines~\ref{line:notloopingA} and \ref{line:notloopingB} can
prove costly depending on the data structure encoding paths. Using
Bloom filters however, this is \TODO{efficient}: it depends on the
number of buckets, and the number of hash functions.

\noindent In terms of convergence time, every $\alpha$ needs to travel
at least its shortest path before termination. Every $\delta$ needs to
reach the border of its partition, triggering an $\alpha$ that fills
the gaps left open by the removal. \TODO{More.}

\paragraph{\TODO{Communication.}}
In terms of number of messages required to reach optimal
partitioning. In the average-case, a process $i$ chosen uniformly at
random among all processes creates a logical partition. Its messages
$\alpha_i$ propagate through the network until reaching processes that
belong to another partition closer to them. This splits partitions in
half in average. Overall, the $a^{th}$ new partition comprises
\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
processes. This decreases every new partition until reaching $0$
processes per new partition: even the chosen process already belongs
to its optimal partition. The average number of messages per process
is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
  more messages (receipt bounded by $|O|$ as well).} Deleting the
$a^{th}$ partition generates the exact same number of messages than
the $a^{th}$ partition creation. \TODO{But what about echos?} In the
worst-case, every new partition includes all but one process belonging
to the previous partition. The total number of messages after the
$a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot a^2)$. As
for the average-case, the number of messages for the partition
deletion is identical to the number of messages of the corresponding
partition creation.

\noindent \TODO{In terms of size of messages.}
